\chapter{Evaluation}
\label{ch:evaluation}

This chapter presents the experimental evaluation to demonstrate the advantages of employing the \sic
quality metric in a stream processing system. All experiments are performed using the \sys prototype
implementation described in Chapter~\ref{ch:system_design}.
The research questions that this chapter addresses aim at a better understanding of the characteristics
of the \sic metric and its applicability in the context of a continuously overloaded stream
processing system.
The \sic metric is designed to be operator agnostic. It can be applied to a general purpose
system supporting any type of query, providing an indication of the quality of the
computed results. This chapter considers the following research questions. Does the \sic value reflect
the correctness of the delivered results? 
What is the correlation between the error of the output and the reduction in \sic values?\\
In addition, the \sic metric is used for the implementation of semantic shedding policies.
We design a fair shedding policy and compare its performance to that of a random
shedder.
Does such a policy achieve better quality results? Is it more fair in the allocation of system
resources?\\
We were also interested in evaluating the performance of such a fair shedding policy in terms of
scalability, both when varying the number of nodes and the number of deployed queries.
What is the behaviour of the fair shedder when the amount of processing resources
changes? Does its performance scale linearly with the number of processing nodes? What happens when the
number of queries is increased on the same processing infrastructure? \\
A user may be willing to trade off the correctness of result with a reduction of costs, \eg by
deploying a larger number of queries on the same processing infrastructure. 
Is it possible to strike a balance between the achieved \sic value and the cost of paying for the
processing infrastructure? Adding an increasing number of queries to the system reduces the cost per
query.
How does this reduction in cost correlate with the reduction in \sic values? All these questions are
answered in this chapter by considering a range of sample queries using both synthetic and real-world
input data.
%\todo{fill page, fix table workload}
%\clearpage


\input{evaluation/61_testbed}  

\input{evaluation/62_correctness}

\input{evaluation/63_shedder}

\input{evaluation/64_cost}

%\input{evaluation/65_stw}

\input{evaluation/66_summary}

