\chapter{DISSP Design}
\label{ch:system_design}

This chapter introduces the design of the DISSP system, a prototype stream processing system developed to
implement and evaluate the quality-centric data model described in the previous chapter. 
The chapter describes some of the novel features of the design and its implementation.
It shows how the system employs the Source Information Content (\sic) metric to \emph{perform efficiently
under overload} and to \emph{provide feedback} to the user about the achieved quality of processing of
queries.

The system is designed from the ground up to be distributed, allowing the processing of queries to
span multiple compute nodes.
It was particularly targeted at environments with a \emph{constrained amount of resources} that can not
easily be scaled. Examples of such deployment settings include \emph{federated resource
pools} with different authorities administering different processing sites; or \emph{cloud deployments}
in which the resources are rented on demand and it may be more cost effective to reduce the
amount of processing resources voluntarily, trading an acceptable reduction in the correctness of results
for a substantially lower operational costs. 

\emph{Overload} is assumed to be the normal condition of operation for the DISSP system and not a
transient, rare event. 
The \sic values of tuples are used to quantify their importance so that the system can perform an 
\emph{intelligent selection} of which tuples to shed. This allows the creation of \emph{flexible shedding
policies}, as will be shown in the next chapter.
This chapter describes the design choices made to provide a reliable and efficient
processing of queries in such a hostile environment.
It also gives an overview of the different system-level components and their interaction when deploying
and running queries. 

%\pagebreak

%--------------------------------------------------------------------------------------------------------

\input{design/41_approach}
%--------------------------------------------------------------------------------------------------------
\input{design/42_basic_components}

%--------------------------------------------------------------------------------------------------------

\input{design/43_sys_arch}

%--------------------------------------------------------------------------------------------------------

\input{design/44_query_deployment}

%--------------------------------------------------------------------------------------------------------

\input{design/45_summary}

	



		

